GVN-hoist: hoisting expressions from control flow

### 2016-08-04 hoist.tex
hoisting too far away

However, in the two special cases discussed in Section-\ref{hoist:reg-pressure},
it will be okay to hoist.

@@

Also, if there are several instructions in between the hoisting point and the
instruction to be hoisted, the instruction to be hoisted crosses several
instructions while hoisting, it means we are adding one register to all the
live-ranges spanning the instructions. That could result in spills.

@@

This means for candidates closer to each other w.r.t. DFS numbers:
\begin{enumerate}
\item would make fewer checks for preconditions.
\item hoisting point will be closer so, the intersection of live-range of the instruction
with other instructions will be minimal.
\end{enumerate}

>>>>

However, in the two special cases discussed in Section-\ref{hoist:reg-pressure},
it will be okay to hoist because the regiter pressure would not change.

@@

Also, if there are several instructions in between the hoisting point and the
instruction to be hoisted, the instruction to be hoisted crosses several
instructions while hoisting, it means we are adding one register to all the
live-ranges spanning the instructions. That could result in spills. In the
current implementation we choose to hoist if the number of instructions crossed
is below a threshold. Ideally, it should be okay to hoist all the instructions
and a later live-range-splitting pass should make the right decision of
rematerializing the instruction should it be beneficial to do so. But the
current live-range splitting pass of llvm is not making the optimial decision
and we have found spills if the threshold is exceeded. The threshold was
computed as a result of tuning the llvm testsuite \cite{llvm-nightly} and spec
benchmark \cite{Henning2000}.

@@

This means for candidates closer to each other w.r.t. DFS numbers:
\begin{enumerate}
\item would make fewer checks for legality and profitability.
\item hoisting point will be closer so, the intersection of live-range of the
  instruction with other instructions will be minimal.
\end{enumerate}
